---
title: "Bella_R_notebook"
output: html_document
date: '2022-08-08'
author: 'Gabriella Fonseca imgabi.com'
editor_options:
  markdown:
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Bellabeat Case Study - Google Data Certification

This document will show the steps followed for the analysis of Bellabeat
data set, as part of the completion of Google's Data Certification
course.

In order to get familiar with working inside the R environment, no other
data software has been used during the process. I tried to add as many
comments as possible so this document can hopefully help other students
as well as serve as a consultation guide for my future self 🙂 🤓

👩‍💻 You can find the "executive version" of the project in my portfolio:
<https://imgabi.com/project-bellabeat/>

❤️ **Please give proper credits if you use my material** ❤️

## 1. Business questions

Bellabeat wants to investigate new opportunities for the development of
marketing initiatives based on the behaviour of current users. For this,
the stakeholders summarised three main areas of investigation:

-   What are some trends in smart device usage?

-   How could these trends apply to Bellabeat customers?

-   How could these trends help influence Bellabeat marketing strategy?

## 2. My approach

My approach starts by investigating trends in the smart device industry.
This will lead the development of more specific questions which I can
investigate with the data sets provided. It is important to mention the
list of questions is a iterative process, so new questions can come up
during the analysis. Nevertheless, having some sort of "map" can be
helpful to organise myself along the way.

Based on my research, I want to:

### A. QUALITY OF DATA

**a1.** How many users are in this data set?

**a2.** What type of data are we analysing? (What do this users track?)

**a3.** What is the date period for the analysis?

**a4.** Is the data tracked automatically or manually?

**a5.** How often do users wear their device?

### B. PROFILE OF USERS

**b1.** What are the average values for this data set?

**b2.** When are users more active? (Possible to break down by day of
week, month?)

**b3.** Link profile of users to current literature

**b4.** Understand if different users groups behave differently

**b5.** Identify segments of users and set a profile for them.

With more clarity on what I need to investigate, I move them to create
my work directory. That is organised as it follows:

> **working directory**
>
> 1.  data
>
> 2.  data_output
>
> 3.  documents
>
> 4.  figure_output
>
> 5.  scripts

All the data I received from Bellabeat is uploaded into the folder
"*data"*. The content of this notebook itself is saved under folder
*"scripts"*.

## 3. Preparing for the analysis

### 3.1 Installing & loading packages

Most of my analysis will require the packages *tidyverse* and *lubridate
(to work with dates)*. Important to remember that the package
*tidyverse* contains in itself the packages *ggplot2, dplyr, tidyr,
readr, purrr, tibble, stringr, forcats*. As I will need most of these
packages, I'd rather install and load *tidyverse* in one go! 🚀

```{r packages, message=FALSE, warning=FALSE}
# install packages
install.packages("tidyverse")
install.packages("lubridate")


#load all packages
library(tidyverse)
library(lubridate)

```

### 3.2 Read the data sets from Bella

Here I decided to name the data frames I would be working with by
starting with the unity they represent. Additional check to confirm if
the number of data sets corresponds to the number in the ZIP files I
received. I had an error so if I hadn't checked this, I'd miss two data
sets in my analysis. Make sure to set the directory accordingly!

I decided to load all the data sets simply to get used with working in
the R environment. At the same time, I like to build the relational
model of the tables I receive, this give me more clarity during the
analysis process. However, for the sake of memory, I removed all the
initial "speak-peak tables" so I can later on load only what I need.

```{r read_datasets}

# For all
# Read file and create data frame
# Check the columns and types with glimpse on some valyes

daily_intensities_df <- read.csv("data/dailyIntensities_merged.csv")
glimpse(daily_intensities_df)

daily_steps_df <- read.csv("data/dailySteps_merged.csv")
glimpse(daily_steps_df)


seconds_heartRate_df <- read.csv("data/heartrate_seconds_merged.csv")
glimpse(seconds_heartRate_df)


hourly_calories_df <- read.csv("data/hourlyCalories_merged.csv")
glimpse(hourly_calories_df)

hourly_intensities_df <- read.csv("data/hourlyIntensities_merged.csv")
glimpse(hourly_intensities_df)

hourly_steps_df <- read.csv("data/hourlySteps_merged.csv")
glimpse(hourly_steps_df)

minute_caloriesNarrow_df <- read.csv("data/minuteCaloriesNarrow_merged.csv")
glimpse(minute_caloriesNarrow_df)


minute_caloriesWide_df <- read.csv("data/minuteCaloriesWide_merged.csv")
glimpse(minute_caloriesWide_df)


minute_intensitiesNarrow_df <- read.csv("data/minuteIntensitiesNarrow_merged.csv")
glimpse(minute_intensitiesNarrow_df)

minute_intensitiesWide_df <- read.csv("data/minuteIntensitiesWide_merged.csv")
glimpse(minute_intensitiesWide_df)

minute_METsNarrow_df <- read.csv("data/minuteMETsNarrow_merged.csv")
glimpse(minute_METsNarrow_df)

minute_sleep_df <- read.csv("data/minuteSleep_merged.csv")
glimpse(minute_sleep_df)

minute_stepsNarrow_df <- read.csv("data/minuteStepsNarrow_merged.csv")
glimpse(minute_stepsNarrow_df)

minute_stepsWide_df <- read.csv("data/minuteStepsWide_merged.csv")
glimpse(minute_stepsWide_df)

daily_sleep_df <- read.csv("data/sleepDay_merged.csv")
glimpse(daily_sleep_df)

weight_logInfo_df <- read.csv("data/weightLogInfo_merged.csv")
glimpse(weight_logInfo_df)


```

[![Model of the data
set](https://imgabi.com/wp-content/uploads/2022/10/bellabeat-google-data-certification-dataset-2048x1274.png)](https://imgabi.com/project-bellabeat#preparing-the-data)

With the drawing of the model, I want to check my hypothesis that some
times have already been clean for me. I assumed that the *narrow tables*
are a cleaned version of the *wide tables.* The following code-block has
a few ways to investigate this matter.

```{r get_to_know_my_data, include=FALSE}

# Here I expect a TRUE Value for the next 3 steps.
# I count the  distinct values for ID in both tables and
# then see if the first group is inside the second one.

# CALORIES
(n_distinct(minute_caloriesNarrow_df$Id)) == (n_distinct(minute_caloriesWide_df$Id)) &&
all(minute_caloriesNarrow_df$Id %in% minute_caloriesWide_df$Id)

# INTENSITIES
(n_distinct(minute_intensitiesNarrow_df$Id)) == (n_distinct(minute_intensitiesWide_df$Id)) &&

all(minute_intensitiesNarrow_df$Id %in% minute_intensitiesWide_df$Id)

# CALORIES
(n_distinct(minute_caloriesWide_df$Id)) == (n_distinct(minute_caloriesNarrow_df$Id)) &&
all(minute_caloriesNarrow_df$Id %in% minute_caloriesWide_df$Id)


# Since all checks came true, I will delete all objects for the sake of memory and create tibbles from now on with the ones I want to use in my analysis
rm(list = ls())

```

### 3.3 Create tibbles for analysis

After getting familiar with the data, I can decide on the data frames I
want to work with. I identified five types of data Sleep, Activity (
with consists of Calories, Steps, Intensities), METs, Heart Rate,
Weight.

I start with creating a tibble for each of them, while performing data
cleaning steps.

```{r setup_tables_analysis}

# NAME CONVENTION
# unitOfTime_tableName

#DAILY ACTIVITY
daily_activity_tb <- tibble(read.csv("data/dailyActivity_merged.csv"))
# check for duplicated entries
sum(duplicated(daily_activity_tb))

#remove duplicates
anyDuplicated(daily_activity_tb)

# check table
glimpse(daily_activity_tb)

# need to convert ActivityDate to Date format
daily_activity_tb <- daily_activity_tb %>%
  mutate(ActivityDate=mdy(ActivityDate))

#some people would now rename columns with lowercase
# I did this first, but decide to skip this step
# since it makes the column names hard to read
# rename_with(daily_activity_tb, tolower)

#move on to do the same
#with sleep and weight so I can merge tables later

#SLEEP
daily_sleep_tb <- tibble(read.csv("data/sleepDay_merged.csv"))

#check for duplicates
sum(duplicated(daily_sleep_tb))

#remove duplicate from data
daily_sleep_tb <- unique(daily_sleep_tb)

#convert date column and names the same as ActivityDate
#convert SleepDay to date and changes the column name to match with previous table
daily_sleep_tb <- daily_sleep_tb %>%
  mutate(SleepDay = as_date(mdy_hms(SleepDay))) %>%
  rename(ActivityDate = SleepDay)

# WEIGHT INFO
weight_info_tb <- tibble(read.csv("data/weightLogInfo_merged.csv"))
glimpse(weight_info_tb)

weight_info_tb <- weight_info_tb %>%
  #because I am only interested in the weight of the day, I can do this conversion to date
  mutate(Date = as_date(mdy_hms(Date))) %>%
  rename(ActivityDate = Date)

sum(duplicated(weight_info_tb))


#MET
#MET is calculated by Minute, so I cannot merge with the previous 3 tables
minute_met_tb <- tibble(read.csv("data/minuteMETsNarrow_merged.csv"))
glimpse(minute_met_tb)

#check for duplicates
sum(duplicated(minute_met_tb))


# HEART
#same as with MET, heart rate is calculated by second, it cannot be merged with 3 first tables
second_heart_rate_tb <- as_tibble(read.csv("data/heartrate_seconds_merged.csv"))

glimpse(second_heart_rate_tb)

second_heart_rate_tb <- second_heart_rate_tb %>%
  mutate(Time=mdy_hms(Time)) %>%
  rename(DayTime = Time)

# the second_heart_rate_tb is quite big, and I was running into memore issues
#so the following two commands are with comments.
# You can try to run them in your environment yourself by removing the #

# check for duplicates
sum(duplicated(second_heart_rate_tb))

#remove duplicate from data
second_heart_rate_tb <- unique(second_heart_rate_tb)

```

With the tables set, I can start the analyses 📊
As I am looking at high-level data, not into a detailed profile for each use,
the daily values and their respective averages are going to be investigated.

## 4. Exploration Data Analysis

### 4.1 Exploring reasons why people use smart watches (Set A)

I will start exploring some basic information in my tibbles. These
explorations are aimed at answering the questions as determined in Set
A.

```{r set_a_users_and_functions}

#A. QUALITY OF DATA

#a1. How many users are in this dataset?
#a2. What type of data are we analysing? (What do this users track?)
#a3. What is the date period for the analysis?
#a4. Is the data tracked automatically or manually?
#a5. How often do users wear their device?


#Check number of distinct users by type of recorded event
n_distinct(daily_activity_tb$Id) #33
n_distinct(daily_sleep_tb$Id) #24
n_distinct(weight_info_tb$Id) #8
n_distinct(minute_met_tb$Id) #33
n_distinct(second_heart_rate_tb$Id) #14

#For the next analysis I need more information about MET, so I will ignore it
remove(minute_met_tb)

#In order to create the graph, I will create a tibble with the values above
users_event <- tribble(
  ~event, ~totalUsers,
  "daily activity", n_distinct(daily_activity_tb$Id),
  "sleep", n_distinct(daily_sleep_tb$Id),
  "weight", n_distinct(weight_info_tb$Id),
  "heart rate", n_distinct(second_heart_rate_tb$Id)
)


glimpse(users_event)

#Bar chart to show different types of events recorded by users.
ggplot(data=users_event,mapping = aes(x = event, y = totalUsers)) +
  #obs: ,stats, needs to be changed to identity because there is no sum being operated
  # we are simply taking the values set byt each event.
  geom_bar(fill="#6186f0", stat="identity") +
  #adds count on the end of the bar for better legibility
  geom_text(aes(label = totalUsers), hjust = -0.5, colour = "#808080")+
  #adds labels
  labs(title = "Total number of users per function",
       caption = "There are five functions offered by the app, but not all of them are used to the same extend.",x= "Function", y= "Total Unique Users") +
  #customise colours of the labels
  theme(
  plot.title = element_text(color="#1c49ab", size=16, face="bold"),
  axis.title.x = element_text(color="#6186f0", size=12, face="bold"),
  axis.title.y = element_text(color="#6186f0", size=12, face="bold"),
  panel.background = element_blank(),
  panel.grid = element_blank(),
  axis.line = element_line(colour = "#000000")
  )+
  #flips coordinates so it is easier to read
  coord_flip()

# Saves recent graph
ggsave("../figure_output/01_types_of_activity_recorded_by_users.png")


# INSIGHTS
# a1. There are 33 users in this data set.
# a2. Users are tracking their daily activity (which includes calores, intensity of activity,and steps.), sleep, MET, heart rate and weight. No all these events are recorded by all users. 


```

I will also produce a Venn Diagram to get an overview of the overlapping
using of functions. For this, I will need to install and load a new
package.

```{r venn_diagram}

#Trying Venn Diagram
#Install and load library
install.packages("VennDiagram")
library(VennDiagram)

# Chart
venn.diagram(
  #passes vectors that will are going to the analysed.
  x = list(daily_activity_tb$Id, daily_sleep_tb$Id, weight_info_tb$Id, second_heart_rate_tb$Id),
  category.names = users_event$event,
  #saves file
  filename = '../figure_output/02_venn_diagramm_user_types.png',
  
  # Output features
  imagetype="png",
  height = 1200,
  width = 1800,
  output=TRUE,
  
  #Format Numbers
  cex = .6,
  fontface = "bold",
  fontfamily = "sans",
  
  # Format categories names
  cat.cex = 0.6,
  cat.fontface = "bold",
  cat.default.pos = "outer",
  cat.fontfamily = "sans",
  
  # Format elipses.
  col=c("#bebada", '#80b1d3', '#8dd3c7', '#b3de69'),
  fill = c(alpha("#bebada",0.3), alpha('#80b1d3',0.3), alpha('#8dd3c7',0.3), alpha('#b3de69',0.3)),
) 

```

I will continue the analysis by merging the tables *daily_sleep* and
*weight_info* to the *daily_activity*. As I observed when I was setting
the model for the data set, *daily_activity* already contains merged
data from *steps*, *calories* and *intensities*.

```{r merging_tables_for_analysis}

# First merge all the 3 tibbles into a new one
bella_tb_daily <- daily_activity_tb %>%
  full_join(daily_sleep_tb) %>%
  full_join(weight_info_tb)

# a quick look at the title
glimpse(bella_tb_daily)

# exclude columns we will not need in the analysis
bella_tb_daily <- bella_tb_daily %>%
  select(-WeightPounds,-LogId, -IsManualReport)

#general stats selecting column, just for practice
bella_tb_daily %>%
  select(TotalSteps, TotalDistance, VeryActiveMinutes:SedentaryMinutes, TotalMinutesAsleep, Calories) %>%
  summary()

#Last but not least, I also want to check the percentage of self-logged activities.
#timespan of data (a3)
n_distinct(bella_tb_daily$ActivityDate)
#from
min(bella_tb_daily$ActivityDate)
#to
max(bella_tb_daily$ActivityDate)
```

After running this block of code I see that of the 33 unique users from
my data set, 24 record sleep data, followed by 14 records for
heart-rate. Weight information is only used by 8 users, being the least
popular function. On top of it, of all the entries from the daily
activity, only 3.4% of recorded represent self-reported data data.

The data was collected over 31 days from 12 April 2016 to 12 May 2016.

From these insights, I can share with my stakeholders that:

-   Most of the data is recorded automatically. Only 3,4% of data is
    recorded manually by users.
-   Users are using the trackers to record their activity automatically,
    followed to monitoring sleep and heart rate.
-   Of the entire data set, only 3 people monitor everything.

### 4.2 Exploring segments and their characteristics (Set B)

#### 4.2.1 Segment 01: User loyalty

The first segment I will explore is how much users wear their devices. I
decided to run the analysis following the classification:

-   **Loyal users:** Data for at least 80% of the days

-   **Casual users:** Data for 50% - 80% of the days

-   **Rare users:** Data for less than 50% of the days

I will look into the monthly averages to analyse the number of steps and
so as to give a profile for each user.

```{r segment_user_loyalty}
#timespan of data
n_distinct(bella_tb_daily$ActivityDate)

#check amount of recorded days by user - 31 days
bella_user_tb <- bella_tb_daily %>%
  group_by(Id) %>%
  summarise(count=n()) %>%
  mutate(type_bella_user = case_when(
    count >= 25 ~ "Loyal",
    count < 25 & count >= 16 ~"Casual",
    count <= 15 ~ "Rare"
  )) %>%
arrange(desc(count))

bella_tb_daily <- bella_user_tb %>%
  select(Id, type_bella_user) %>%
  inner_join(bella_tb_daily)

bella_tb_daily %>%
  group_by(type_bella_user, Id) %>%
  summarise(count = n())

#Creates a factor for loyalty,
# so in graphs it will be ordered from loyal to rare user
bella_tb_daily$type_bella_user <- factor(bella_tb_daily$type_bella_user,levels = c("Loyal", "Casual", "Rare"))

# counts the type of bella user
bella_tb_daily %>% 
  group_by(type_bella_user) %>%
  summarise(count = n_distinct(Id),
            percentage = count/n_distinct(bella_tb_daily$Id)*100) %>%
  #Here I will draw a pie chart with the types of users
  ggplot(aes(x="", y=count, fill=type_bella_user)) +
  #I need to set the geom bar and add the coord_polar to transform the graph from bar to pie
  geom_bar(width = 1, stat = "identity")+
  coord_polar("y", start=0)+
  #change fill colours
  scale_fill_manual(values=c("#b3de69", '#ffffb3', '#fb8072')) +
  #adds labels
  labs(title = "User profile: Loyalty", caption = "Based on a sample of 33 users for 31 days - April to May 2016.") +
  #adds labels with count
  geom_label(aes(label = count), color = "#1c49ab", position = position_stack(vjust = 0.5),show.legend = FALSE)+
  #Customise legend
  guides(fill = guide_legend(title = "Type of Bellabeat user"))+
  #customise colours of the labels
  theme(
  plot.title = element_text(color="#1c49ab", size=16, face="bold"),
  panel.grid = element_blank(),
  panel.background = element_blank(),
  axis.line = element_blank(),
  axis.text  = element_blank(),
  axis.title = element_blank()
  )

# Saves recent graph
ggsave("../figure_output/03_user_profile_loyalty.png")


```

These stats tell me something about my sample: **Most users of this
sample (88%) use the smart watch with high frequency, or more than 80%
of the time (25-31 days)**.

#### 4.2.2 Segment 02: Risk of premature death & Number of steps

Literature suggests the following regarding the daily optimal number of
steps and risk of premature death:

-   At least 7,000 steps reduces the chances of premature death
-   4,400 is enough to reduce the risk of death considerably

Therefore, I created the following classification:

-   **Less than 4,400 steps:** High risk

-   **Between 4,400 - 7,000 steps:** Medium risk

-   **More than 7,000 steps:** Low risk

```{r segment_risk_premature_death}

# create new tibble with averages by user
user_type_tb <- bella_tb_daily %>%
  group_by(Id) %>%
  summarise(mean_daily_steps = mean (TotalSteps),
            mean_calories = mean (Calories),
            mean_sleep_minutes= mean (TotalMinutesAsleep),
            mean_very_active_minutes = mean(VeryActiveMinutes),
            mean_fairly_active_minutes = mean(FairlyActiveMinutes),
            mean_lightly_active_minutes= mean(LightlyActiveMinutes),
            mean_sedentary_minutes = mean(SedentaryMinutes),
            count_records=n())

# create new column in user_type based on their risk and number of steps
user_type_tb <- user_type_tb %>%
  mutate(premature_death_risk = case_when(
    mean_daily_steps < 4400 ~ "High risk",
    mean_daily_steps >= 4400 & mean_daily_steps < 7000 ~ "Medium risk",
    mean_daily_steps >= 7000 ~ "Low risk"
  ))

#glimpses at the tibble
glimpse(user_type_tb)

#Creates a factor for premature risk level,
# so in graphs it will be ordered from high to low risk level
user_type_tb$premature_death_risk <- factor(user_type_tb$premature_death_risk,levels = c("Low risk", "Medium risk", "High risk"))

#shows the distribution of the amount of recorded days by user
# this graph is okay to help me understand my data, but I don't want
# to present it, so I don't need to work on its visuals
ggplot(user_type_tb)+
  geom_histogram(aes(x=count_records), binwidth = 5)

#shows the distribution of type of user
# this graph is okay, but the boxplot in the end might be better
# as it also shows the mean and variations while the size of the groups
ggplot(user_type_tb)+
  geom_bar(aes(x=premature_death_risk)) 


# distribution of steps and calories by user premature risk group
ggplot(user_type_tb)+
  geom_point(aes(x=mean_daily_steps, y=mean_calories,colour=premature_death_risk))+
  #adds labels
  labs(title = "Relationship between Calories and Daily Steps", y= "Calories",  x="Daily Steps", fill="Risk of Premature Death") +
  #customise colours of the labels
  theme(
  plot.title = element_text(color="#1c49ab", size=16, face="bold"),
  axis.title = element_text(color="#6186f0", size=12, face="bold"),
  panel.background = element_blank(),
  panel.grid = element_blank(),
  axis.line = element_line(colour = "#000000") 
  ) +
  #change fill colours
  scale_fill_manual(values=c("#b3de69", '#ffffb3', '#fb8072'))

# Saves recent graph
ggsave("../figure_output/04_user_profile_loyalty_calories_steps_scatterplot.png")


# but this representation is better because I can see the averages and the size of each group
# so in my presentation I will use this one

ggplot(user_type_tb)+
  geom_boxplot(aes(y=mean_daily_steps, group=premature_death_risk, fill=premature_death_risk)) +
  #adds labels
  labs(title = "Daily Steps for Risk of Premature Death", y= "Daily Steps", fill="Risk of Premature Death") +
  #customise colours of the labels
  theme(
  plot.title = element_text(color="#1c49ab", size=16, face="bold"),
  axis.title = element_text(color="#6186f0", size=12, face="bold"),
  panel.background = element_blank(),
  panel.grid = element_blank(),
  axis.line = element_line(colour = "#000000"),
  axis.title.x = element_blank(),
  axis.text.x = element_blank()
  )+
  #change fill colours
  scale_fill_manual(values=c("#b3de69", '#ffffb3', '#fb8072'))

# Saves recent graph
ggsave("../figure_output/05_user_profile_loyalty_steps_boxplot.png")

```

These stats show my that the majority of my sample has a low risk of
premature death due to their average number of steps. It also seems that
there is a relationship between premature death and the calories and
daily steps for individuals. However I still need to verify this with
the appropriate statistical methods (which is done in section 4.4).

#### 4.2.3 Segment 03: Fit level

The literature has different recommendations regarding fitness levels:

-   30 minutes of brisk activity in all or most days of the week
-   150 minutes of moderate activity per week
-   If you seat for over 8 hours, 60-75 minutes of moderate activity

Based on this, I created the following classification for fit level:

-   **Fit:** The average movement level of the last 30 days is equal or
    higher to 30 minutes

-   **Fairly active:** The number for active minutes needs to be equal
    or higher than 60 for individuals who spend 8 hours or more sitting;
    or if an individual has less than 8 hours sitting per day

-   **Sedentary:** For individuals with more than 8 hours sitting and
    less than 60 minutes of active or fairly active activity

```{r segment_fit_level}

user_type_tb

#create classification
user_type_tb <- user_type_tb %>%
  mutate(fit_profile = case_when(
    mean_very_active_minutes >= 30 ~ "Fit",
    mean_sedentary_minutes >= 480 & mean_very_active_minutes + mean_fairly_active_minutes <= 60 ~ "Sedentary",
    TRUE  ~ "Fairly Active"
    )) 

glimpse(user_type_tb)


#Creates a factor for premature risk level,
# so in graphs it will be ordered from high to low risk level
user_type_tb$fit_profile <- factor(user_type_tb$fit_profile,levels = c("Fit", "Fairly Active", "Sedentary"))


# fit profile users check
user_type_tb %>%
  group_by(fit_profile) %>%
  summarise(count = n(),
            active_min = mean(mean_very_active_minutes),
            sedentary_min = mean(mean_sedentary_minutes))

#Here I can see we have a large number of users who stay sitting a long time during the day. The averages in the fit group show that they also sit for longer periods of time, but they compensate it by intensive periods of exercise

#Let's plot a graph to explain this to the stakeholders.
#First I want to cause impact and show the large number of sedentary people
# so I will create a Pie Chart

# counts the type of bella user
user_type_tb %>%
  group_by(fit_profile) %>%
  summarise(count = n()) %>%
  #Here I will draw a pie chart with the types of users
  ggplot(aes(x="", y=count, fill=fit_profile)) +
  #I need to set the geom bar and add the coord_polar to transform the graph from bar to pie
  geom_bar(width = 1, stat = "identity")+
  coord_polar("y", start=0)+
  #change fill colours
  scale_fill_manual(values=c("#b3de69", '#ffffb3', '#fb8072')) +
  #adds labels
  labs(title = "User profile: Fitness", caption = "Based on a sample of 33 users for 31 days - April to May 2016.") +
  #adds labels with count
  geom_label(aes(label = count), color = "#1c49ab", position = position_stack(vjust = 0.5),show.legend = FALSE)+
  #Customise legend
  guides(fill = guide_legend(title = "Fitness level"))+
  #customise colours of the labels
  theme(
  plot.title = element_text(color="#1c49ab", size=16, face="bold"),
  panel.grid = element_blank(),
  panel.background = element_blank(),
  axis.line = element_blank(),
  axis.text  = element_blank(),
  axis.title = element_blank()
  )

# Saves recent graph
ggsave("../figure_output/06_user_profile_fitness.png")


#Now I want to show how their fitness level and their averages
ggplot(user_type_tb)+
  geom_boxplot(aes(y=mean_sedentary_minutes, group=fit_profile, fill=fit_profile)) +
  geom_boxplot(aes(y=mean_very_active_minutes, group=fit_profile, fill=fit_profile)) +
  #adds labels
  labs(title = "Sedentary and Active Minutes for Fitness Level", y= "Minutes", fill="Fitness Level",
       caption = "The blocks on the top of the image represent sedentary minutes; 
       The blocks on the bottom of the image represent very active minutes.") +
    geom_hline(yintercept = 500) +
  #customise colours of the labels
  theme(
  plot.title = element_text(color="#1c49ab", size=16, face="bold"),
  axis.title = element_text(color="#6186f0", size=12, face="bold"),
  panel.background = element_blank(),
  panel.grid = element_blank(),
  axis.line = element_line(colour = "#000000"),
  axis.title.x = element_blank(),
  axis.text.x = element_blank()
  )+
  #change fill colours
  scale_fill_manual(values=c("#b3de69", '#ffffb3', '#fb8072'))

# Saves recent graph
ggsave("../figure_output/07_user_profile_fitness_sedentary_active_minutes.png")

```

After plotting the last graph, I can see that most users can be
classified as sedentary. This seems quite strange to me considering the
analysis on the number of steps we saw earlier. So I decided to dig
deeper into the data and I noticed several users have '1440 minutes' of
sedentary activity in some days. That means they would have spent 24
hours sitting! As I cannot ask the data providers how the sedentary
minutes are calculated, and its relationship with sleep time, I decided
not to user these last graphs in my presentation. It is always important
to be cautious and do not assume things we don't know.

### 4.3 Explorations for patterns

Now I will move on looking for patterns in the data.

```{r pattern_day_week}

# let me remind myself of the daya in the table
glimpse(bella_tb_daily)

# I will create a new column with the day of the week
# based on my column ActivityDate
bella_tb_daily <- bella_tb_daily %>%
  mutate(
    WeekDay = weekdays(ActivityDate)
  )

# create a factor for days of the week, so they are organise properly
bella_tb_daily$WeekDay <- factor(bella_tb_daily$WeekDay,
                                 levels = c("Monday", "Tuesday", "Wednesday", "Thursday",
                                            "Friday", "Saturday", "Sunday" ))


# visualise the graph for total steps and calories
ggplot(bella_tb_daily)+
  geom_jitter(aes(y=TotalSteps, x=Calories, colour=WeekDay)) +
  facet_wrap(~ WeekDay)
# I can see some "extra steps" on saturdays, but nothing conclusive

# Days of the week and steps
ggplot(bella_tb_daily, aes(WeekDay, TotalSteps))+
  geom_bar(stat = "summary_bin", fun = mean, fill="#6186f0") +
  #two lines to intercept values for sedentary and ideal number of steps
  geom_hline(yintercept = 4400, colour="red") +
  geom_hline(yintercept = 7000) +
  labs(title = "Total Steps per Day of the Week", caption = "Based on a sample of 33 users for 31 days - April to May 2016.", y="Average Number of Steps", x= "") +
  theme(
  plot.title = element_text(color="#1c49ab", size=16, face="bold"),
  axis.title = element_text(color="#6186f0", size=12, face="bold"),
  panel.grid = element_line(color="#cccccc"),
  panel.background = element_blank(),
  axis.line = element_blank() 
  )

# Saves recent graph
ggsave("../figure_output/08_steps_day_week_all.png")


# Days of the week and calories
ggplot(bella_tb_daily, aes(WeekDay, Calories))+
  geom_bar(stat = "summary_bin", fun = mean, fill="#6186f0") +
  #line to intercept average calories for adult
  geom_hline(yintercept = 2200, colour="red") +
  labs(title = "Total Calories per Day of the Week", caption = "Based on a sample of 33 users for 31 days - April to May 2016.", y="Average Calories", x= "") +
  theme(
  plot.title = element_text(color="#1c49ab", size=16, face="bold"),
  axis.title = element_text(color="#6186f0", size=12, face="bold"),
  panel.grid = element_line(color="#cccccc"),
  panel.background = element_blank(),
  axis.line = element_blank() 
  )

# Saves recent graph
ggsave("../figure_output/09_calories_day_week_all.png")

# Days of the week and sleep
ggplot(bella_tb_daily, aes(WeekDay, TotalMinutesAsleep))+
  geom_bar(stat = "summary_bin", fun = mean, fill="#6186f0") +
  # intercept the line for sleeping value (at least 7 hours or 420 minutes, max 9 hours)
  geom_hline(yintercept = 420, colour="red") +
  geom_hline(yintercept = 540, colour="blue") +
    labs(title = "Sleep Minutes per Day of the Week", caption = "Based on a sample of 33 users for 31 days - April to May 2016.", y="Average Sleep Minutes", x= "") +
  theme(
  plot.title = element_text(color="#1c49ab", size=16, face="bold"),
  axis.title = element_text(color="#6186f0", size=12, face="bold"),
  panel.grid = element_line(color="#cccccc"),
  panel.background = element_blank(),
  axis.line = element_blank()
  )


# Saves recent graph
ggsave("../figure_output/10_sleep_day_week_all.png")

```

From the graphs above, I observe that the number of steps and calories
is somehow constant among users. I can also see users are not sleeping
the recommended amount of 7 hours. But would this behaviour stay the
same if I consider the different types of users? Let's find out!

```{r pattern_day_week_groups}

# STEPS
# Days of the week and steps // Loyalty Groups
ggplot(bella_tb_daily, aes(WeekDay, TotalSteps))+
  geom_bar(stat = "summary_bin", fun = mean, fill="#6186f0") +
  #two lines to intercept values for sedentary and ideal number of steps
  geom_hline(yintercept = 4400, colour="red") +
  geom_hline(yintercept = 7000) +
  labs(title = "Total Steps per Day of the Week / Loyalty Groups", caption = "Based on a sample of 33 users for 31 days - April to May 2016.", y="Average Number of Steps", x= "") +
  theme(
  plot.title = element_text(color="#1c49ab", size=16, face="bold"),
  axis.title = element_text(color="#6186f0", size=12, face="bold"),
  panel.grid = element_line(color="#cccccc"),
  panel.background = element_blank(),
  axis.line = element_blank(),
  axis.text.x = element_text(angle= 90, size= 10)
  ) +
  facet_wrap( ~type_bella_user)

# Saves recent graph
ggsave("../figure_output/10_steps_day_week_bella_user_type.png")


# add premature death risk to tb
bella_tb_daily <- user_type_tb %>%
  select(Id, premature_death_risk) %>%
  inner_join(bella_tb_daily)


# Days of the week and steps // Premature Death Risk
ggplot(bella_tb_daily, aes(WeekDay, TotalSteps))+
  geom_bar(stat = "summary_bin", fun = mean, fill="#6186f0") +
  #two lines to intercept values for sedentary and ideal number of steps
  geom_hline(yintercept = 4400, colour="red") +
  geom_hline(yintercept = 7000) +
  labs(title = "Total Steps per Day of the Week / Premature Death Risk", caption = "Based on a sample of 33 users for 31 days - April to May 2016.", y="Average Number of Steps", x= "") +
  theme(
  plot.title = element_text(color="#1c49ab", size=16, face="bold"),
  axis.title = element_text(color="#6186f0", size=12, face="bold"),
  panel.grid = element_line(color="#cccccc"),
  panel.background = element_blank(),
  axis.line = element_blank(),
  axis.text.x = element_text(angle= 90, size= 10)
  ) +
  facet_wrap( ~premature_death_risk)


# Saves recent graph
ggsave("../figure_output/11_steps_day_week_bella_user_death_risk.png")


#############################################################################
# CALORIES

# Days of the week and calories // Loyalty Groups
ggplot(bella_tb_daily, aes(WeekDay, Calories))+
  geom_bar(stat = "summary_bin", fun = mean, fill="#6186f0") +
  #line to intercept average calories for adult
  geom_hline(yintercept = 2200, colour="red") +
  labs(title = "Total Calories per Day of the Week / Loyalty Groups", caption = "Based on a sample of 33 users for 31 days - April to May 2016.", y="Average Calories", x= "") +
  theme(
  plot.title = element_text(color="#1c49ab", size=16, face="bold"),
  axis.title = element_text(color="#6186f0", size=12, face="bold"),
  panel.grid = element_line(color="#cccccc"),
  panel.background = element_blank(),
  axis.line = element_blank() ,
  axis.text.x = element_text(angle= 90, size= 10)
  ) + 
  facet_wrap( ~type_bella_user)

# Saves recent graph
ggsave("../figure_output/12_calories_day_week_bella_user_type.png")



# Days of the week and calories // Premature Death Risk
ggplot(bella_tb_daily, aes(WeekDay, Calories))+
  geom_bar(stat = "summary_bin", fun = mean, fill="#6186f0") +
  #line to intercept average calories for adult
  geom_hline(yintercept = 2200, colour="red") +
  labs(title = "Total Calories per Day of the Week / Premature Death Risk", caption = "Based on a sample of 33 users for 31 days - April to May 2016.", y="Average Calories", x= "") +
  theme(
  plot.title = element_text(color="#1c49ab", size=16, face="bold"),
  axis.title = element_text(color="#6186f0", size=12, face="bold"),
  panel.grid = element_line(color="#cccccc"),
  panel.background = element_blank(),
  axis.line = element_blank() ,
  axis.text.x = element_text(angle= 90, size= 10)
  ) +
  facet_wrap( ~premature_death_risk)

# Saves recent graph
ggsave("../figure_output/13_calories_day_week_bella_user_death_risk.png")


###################################################################################
# SLEEP
# Days of the week and sleep / Loyalty Groups
ggplot(bella_tb_daily, aes(WeekDay, TotalMinutesAsleep))+
  geom_bar(stat = "summary_bin", fun = mean, fill="#6186f0") +
  # intercept the line for sleeping value (at least 7 hours or 420 minutes, max 9 hours)
  geom_hline(yintercept = 420, colour="red") +
  geom_hline(yintercept = 540, colour="blue") +
    labs(title = "Sleep Minutes per Day of the Week / Loyalty Groups", caption = "Based on a sample of 33 users for 31 days - April to May 2016.", y="Average Sleep Minutes", x= "") +
  theme(
  plot.title = element_text(color="#1c49ab", size=16, face="bold"),
  axis.title = element_text(color="#6186f0", size=12, face="bold"),
  panel.grid = element_line(color="#cccccc"),
  panel.background = element_blank(),
  axis.line = element_blank() ,
  axis.text.x = element_text(angle= 90, size= 10)
  ) + 
  facet_wrap( ~type_bella_user)


# Saves recent graph
ggsave("../figure_output/14_sleep_day_week_bella_user_type.png")



# Days of the week and sleep / Premature Death Risk
ggplot(bella_tb_daily, aes(WeekDay, TotalMinutesAsleep))+
  geom_bar(stat = "summary_bin", fun = mean, fill="#6186f0") +
  # intercept the line for sleeping value (at least 7 hours or 420 minutes, max 9 hours)
  geom_hline(yintercept = 420, colour="red") +
  geom_hline(yintercept = 540, colour="blue") +
    labs(title = "Sleep Minutes per Day of the Week / Premature Death Risk", caption = "Based on a sample of 33 users for 31 days - April to May 2016.", y="Average Sleep Minutes", x= "") +
  theme(
  plot.title = element_text(color="#1c49ab", size=16, face="bold"),
  axis.title = element_text(color="#6186f0", size=12, face="bold"),
  panel.grid = element_line(color="#cccccc"),
  panel.background = element_blank(),
  axis.line = element_blank() ,
  axis.text.x = element_text(angle= 90, size= 10)
  ) + 
  facet_wrap( ~premature_death_risk)


# Saves recent graph
ggsave("../figure_output/15_sleep_day_week_bella_user_death_risk.png")

```

With the graphs above I can see that the total number of steps is more
constant for Loyal users when compared to Casual and Rare users. I see a
similar behaviour if I breakdown my users into groups with different
risks of premature death. Users with a low risk of premature death
perform in average more than 7,700 steps for every day of the week.

Users with low risk of premature death spend more calories in average
than the other groups, who do not even reach the minimum of 2200
calories/spent to maintain their weight. Again, the trend is similar for
Loyalty groups: Loyal users consumer more calories than the other two
groups.

Lastly, we can see that the number of minutes sleep is somewhat constant
through the week for individuals classified as loyal users. Casual users
sleep more on Sundays. We have not enough data for Rare users. In terms
of premature death risk, users with low risk of death sleep less than
the other groups, however the differences are not too big. In any case,
we will check for statistically different results in the following
section.

### 4.4 Statistical tests for correlation

With this, we arrive at the most complex part of the analysis: We will
check if the results we observed above are statistically significant or
if they happened by chance.

There are many statistical tests you can use, and it will all depend on
the types of variables you are comparing and how your sample behaves. I
will assume you have a basic knowledge in this area, but nevertheless,
the links below are always useful:

-   <https://statsandr.com/blog/what-statistical-test-should-i-do/>

-   <https://statsandr.com/blog/files/overview-statistical-tests-statsandr.pdf>

-   <https://www.statsflowchart.co.uk/>

We will start with some simple correlation tests for our continuous
variables (Minutes sleep, Calories and Steps).

```{r simple_correlation}

# The first thing I need to do, is to test for normality
# because this will interfere with the type of tests I need to run
# REFENCES FOR CORRELATION PLOT: https://r-coder.com/correlation-plot-r/

# Tests for normality | Shapiro Test
#if p–value is greater than 0.05, so we can assume the normality
 shapiro.test(bella_tb_daily$TotalSteps)
 shapiro.test(bella_tb_daily$TotalMinutesAsleep)
 shapiro.test(bella_tb_daily$Calories)

#as all p values are lower than 0.05, we can't assume these distributions are normal
#Therefore, Spearman’s coefficient is considered more appropriate than Pearson’s for skewed distributions (Mukaka, 2012)
# For all the correlations, I need p lower than 0.05 for statistical significant results
#SLEEP AND STEPS

 cor.test(bella_tb_daily$TotalSteps, bella_tb_daily$TotalMinutesAsleep, use="pairwise.complete.obs", method = "spearman")  # pairwise function eliminates the NA values

 # plot the graph to have a visual representation
 bella_tb_daily %>%
   ggplot(aes(x = TotalSteps, y = TotalMinutesAsleep)) +
   geom_jitter() +
   geom_smooth(method = "lm", se =TRUE, color = 'red') +
   labs(title = "Correlation between Total Steps and Minutes Asleep", caption = "Based on a sample of 33 users for 31 days - April to May 2016.", x = "Steps", y="Minutes Asleep") +
  theme(
  plot.title = element_text(color="#1c49ab", size=16, face="bold"),
  axis.title = element_text(color="#6186f0", size=12, face="bold"),
  panel.grid = element_line(color="#cccccc"),
  panel.background = element_blank(),
  axis.line = element_blank() ,
  axis.text.x = element_text(angle= 45, size= 10)
  )

 ggsave("../figure_output/16_correlation_steps_sleep.png")

# S = 14066506, p-value = 4.382e-06
# rho =  -0.2245838 

 
 ##################################
 
 #SLEEP AND CALORIES
 cor.test(bella_tb_daily$Calories, bella_tb_daily$TotalMinutesAsleep, use="pairwise.complete.obs", method = "spearman")
 
 #S = 11929269, p-value = 0.4366
 # rho = - -0.03852297
 
  bella_tb_daily %>%
   ggplot(aes(x = Calories, y = TotalMinutesAsleep)) + 
   geom_jitter()+ 
   geom_smooth(method = "lm", se =TRUE, color = 'red')+
      labs(title = "Correlation between Calories and Minutes Asleep", caption = "Based on a sample of 33 users for 31 days - April to May 2016.", x = "Calories", y="Minutes Asleep") +
  theme(
  plot.title = element_text(color="#1c49ab", size=16, face="bold"),
  axis.title = element_text(color="#6186f0", size=12, face="bold"),
  panel.grid = element_line(color="#cccccc"),
  panel.background = element_blank(),
  axis.line = element_blank() ,
  axis.text.x = element_text(angle= 45, size= 10)
  ) 
  
 ggsave("../figure_output/17_correlation_calories_sleep.png")
 
##########################
  
 
 #CALORIES AND STEPS
  cor.test(bella_tb_daily$Calories, bella_tb_daily$TotalSteps, use="pairwise.complete.obs", method = "spearman")
 
   
  #p = -2.2e-16
  #rho = 0.5592

  bella_tb_daily %>%
   ggplot(aes(x = Calories, y = TotalSteps)) + 
   geom_point() + 
   geom_smooth(method = "lm", se =TRUE, color = 'red') +
   labs(title = "Correlation between Calories and Steps", caption = "Based on a sample of 33 users for 31 days - April to May 2016.", x = "Calories", y="Steps") +
  theme(
  plot.title = element_text(color="#1c49ab", size=16, face="bold"),
  axis.title = element_text(color="#6186f0", size=12, face="bold"),
  panel.grid = element_line(color="#cccccc"),
  panel.background = element_blank(),
  axis.line = element_blank() ,
  axis.text.x = element_text(angle= 45, size= 10)
  ) 
  

   ggsave("../figure_output/18_correlation_steps_calories.png")


#######################################

```

From these results I can see that there is a statistical significant
monotonic relationship between Calories and Steps with moderate
strength. This means that when the number of Calories increases, so does
the number of steps.

As for Sleep and Calories, although the relationship exists, it is
considered weak.

The interpretation of the coefficients follows research from Akoglu
(2018) and it is represented on the table below:

| Association strength | Modular Value \| r \| |
|----------------------|-----------------------|
| Strong               | \> 6                  |
| Moderate             | \<= 6 && \>3          |
| Weak                 | \<= 3                 |

I have some values already, but should we go even further and look at
all the numeric values we have in the daily data set? For this I will
work with a correlation matrix.

```{r correlation_matrix}

#Install package
install.packages("corrplot")
library(corrplot)
?corrplot

#Great tutorials on this package: 
# https://r-coder.com/correlation-plot-r/
# https://cran.r-project.org/web/packages/corrplot/vignettes/corrplot-intro.html

#prepare bella table by removing columns I don't need
# I will also drop NA otherwise the matrix doesn't work
cor_bella_tb_daily <- bella_tb_daily %>%
  select(TotalSteps:TotalMinutesAsleep) %>%
  select(-TotalSleepRecords) %>%
  drop_na()


# because the corrplot is not part of ggplot, I need to find another way to save this file
#this will be done with the following + dev.off() after the graph is plotted
png(height=1200, width=1200, file="../figure_output/19_correlation_matrix.png")

corrplot(cor(cor_bella_tb_daily, method = c("spearman")), # Correlation matrix
         type = "upper",  # Correlation plot style (also "upper" and "lower")
         order = "original", #order of the variables
         diag = FALSE, # If TRUE (default), adds the diagonal where cor=1
         sig.level = .05, #significance level
         addCoef.col ='#3f3f3f', #text inside colour
         number.cex= 1, #text label size
         tl.col = "black", # Labels color
         title = "Correlation Matrix - Daily Values",       # Main title
         tl.srt = 45, #rotation
         tl.cex = 1.2,  #font size
         method="number") #how I want to populate the values. As there are many, numbers are easier to read

dev.off()


```

From this correlation matrix I can infer that the *Distances* and
*ActivityTypes* are strongly correlated (for example, VeryActiveDistance
is correlated to VeryActiveMinutes (r=0.97). This is not the same for
Sedentary though, but we had already seen that something was unclear on
how Sedentary is calculated based on the results in section 4.2.3.

Additionally, Calories has a moderate association with Total Distance
and Very Active Minutes, while Total Steps and Total Distance has very
strong association (which is not a surprise!)

Important to clarify that the values are slightly different than the
ones we had in the first correlation tests due to the number of
observations. For the correlation matrix, I already dropped all columns
with a NA value before the tests, while the first set of correlation
tests only drops a value based on the observation pair.

Moving on, I want to see if the differences between groups which I
observed in section 4.3 are statistically significant. As here I am
working with both categorical and continuous variables, I can no longer
use the correlation test from the examples above. Additionally, as not
to make any assumptions on my data (and considering we already saw there
is no normal distribution for Calories, Sleep and Steps), I will move on
with a non-parametric test named: Kruskal-Wallis test.

```{r kruskal_tests}

#More info on the Kruskal tests: 
#. https://statsandr.com/blog/kruskal-wallis-test-nonparametric-version-anova/
#. http://www.sthda.com/english/wiki/kruskal-wallis-test-in-r 

# I am looking for p values < 0.05
#premature death risk and calories
kruskal.test(premature_death_risk ~ mean_calories,
  data = user_type_tb
)

#p-value = 0.4667

########

#premature death risk and daily steps
kruskal.test(premature_death_risk ~ mean_daily_steps,
  data = user_type_tb
)

#p-value = 0.4667

########
#premature death risk and sleep
kruskal.test(premature_death_risk ~ mean_sleep_minutes,
  data = user_type_tb
)



#type bella user and daily steps
kruskal.test(type_bella_user ~ mean_calories,
  data = user_type_tb
)

#type bella user and calories
kruskal.test(type_bella_user ~ mean_daily_steps,
  data = user_type_tb
)


#type bella user and sleep
kruskal.test(type_bella_user ~ mean_sleep_minutes,
  data = user_type_tb
)


#steps and weekdays
kruskal.test(WeekDay ~ TotalSteps,
  data = bella_tb_daily
)

kruskal.test(WeekDay ~ Calories,
  data = bella_tb_daily
)

kruskal.test(WeekDay ~ TotalMinutesAsleep,
  data = bella_tb_daily
)

```

As you can see, none of the tests above returned a value of p\<0.05,
therefore the differences observed in terms of groups and also days of
the week cannot be used for generalisation. We can still present them to
the stakeholders, but it is important to make clear that no statistical
difference was found.

Last but not least, I will compare the two group classifications I
created by using a contingency table.

```{r mosaic_and_contigency_table}

# More infor on contingency tables
# https://r-coder.com/contingency-table-r/

# install package
library(vcd)

#prepare table by including the type of bella user
user_type_tb <- bella_user_tb %>%
  inner_join(user_type_tb)

#create factor
user_type_tb$type_bella_user <- factor(user_type_tb$type_bella_user,levels = c("Loyal", "Casual", "Rare"))

# Sees how users are distributed in two groups
tbl <- xtabs(~premature_death_risk + type_bella_user, user_type_tb)
ftable(tbl)

# simple mosaic
mosaic(tbl, main = "Bellabeat Users Breakdown")

# learn more about mosaic functions
?mosaic


# create a more fancy mosaic which I can save
png(height=1200, width=1200, file="../figure_output/20_mosaic_user_type_breakdown.png")

mosaic(tbl, 
       shade = TRUE,
       legend = TRUE,
       labeling_args = list(set_varnames = c(type_bella_user = "Loyalty",
                                             premature_death_risk = "Risk of Premature Death"
                                             )
                            ),
       set_labels = list(
                         type_bella_user = c("L", "C", "R"),
                         premature_death_risk = c("L", "M", "H")
                         ),
       main = "Bellabeat Users Breakdown")

dev.off()
```

From this graph we see that there is no statistical significant
relationship between the groups (p \> 0.05)

However I can still share with my stakeholders that: Most users are
considered loyal, with a low risk of premature death (19/33). We have
however 5 users with Medium risk and 5 with High risk.

## 5. Conclusions and recommendations

It was a long way and now we have many insights and 20 graphs in our
folder! We don't have to share all of them. Instead, I created a
presentation with the most important one, which you can find here:

If you arrive here, try to run your own analysis and come up to your own
conclusions. Let me know later on if there is something unclear or if
you have taken another approach to the analysis.

**Knowledge is more when it is shared ❤️**

## 6. References

Akoglu, H. (2018). User's guide to correlation coefficients. Turkish
Journal of Emergency Medicine, 18(3), 91--93.
<https://doi.org/10.1016/j.tjem.2018.08.001>

Mukaka, M. M. (2012). A guide to appropriate use of correlation
coefficient in medical research. Malawi Medical Journal : The Journal of
Medical Association of Malawi, 24(3), 69--71.
<https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3576830/>

## 7. Downloads

-   You can download this set and reproduce it on your machine here:
-   You can find the project description and presentation with slides
    here: <https://imgabi.com/project-bellabeat/>
-   Let's connect on Linkedin:
    <https://linkedin.com/in/gabriellafonsecaribeiro>
-   I am also sharing memes on Twitter:
    <https://twitter.com/imgabidotcom>
